### 2014-05-21 ApTranscriptome_TR.Rmd
Some updates

Genes with increased expression at *High* temperatures are on average turned on 2.5°C higher in *ApVT* than *AcNC*.

@@

Genes with increased expression at *Low* temperatures are on average turned on 1°C higher in *ApVT* than *AcNC*.

@@

```{r plot_low_T_on, echo=FALSE, eval=TRUE}
# merge data for plotting
Ap.T_on <- rbind(A22.high.T_on, Ar.high.T_on, A22.low.T_on, Ar.low.T_on)

@@

Next, I partition the differences in the reaction norms into the variation explained by differences in the trait means and slope, as curvature and wiggle did not differ between species. To do this, I first standardize each of these parameters so they are directly comparable.

@@

```{r extract_Transcripts}
A22.only.high <- Ap.response.type[which(Ap.response.type$A22.type == "High" & Ap.response.type$Ar.type != "High"), "Transcript"]
Ar.only.high <- Ap.response.type[which(Ap.response.type$A22.type != "High" & Ap.response.type$Ar.type == "High"), "Transcript"]

@@

for(i in unique(A22.low.Ar.int.TPM.dt.sub$Transcript)[1:10]) {
    s <- A22.low.Ar.int.TPM.dt.sub[i]
    X11()
    plot(s$val, s$pTPM, ylim = c(0, max(s$pTPM)+.1))
    points(s$val, s$TPM, pch = 8, col = "red")
    if(s[which(s$val == 38.5) , pTPM] == min(s$pTPM)) print("OffHigh") else {
        print("OnLow")
    }
}

#    if(min(s[which(s$val < 30) , pTPM]) < s[which(s$val == 38.5), pTPM] & s[which(s$val == 0), pTPM] < (s[which(s$val == 21), pTPM] + sd(s$pTPM))) print("On low") else {

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, tt2, tt3, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, Ap.gsea1, Ap.setdiff.gsea, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.themsens, t.thermbreadth, file = "ms.RData")
```

>>>>

Genes with increased expression at *High* temperatures are on average turned on 1°C higher in *AcNC* than *ApVT*.

@@

Genes with increased expression at *Low* temperatures are on average turned on 0.2°C higher in *ApVT* than *AcNC*.

@@

```{r plot_T_on, echo=FALSE, eval=TRUE}
# merge data for plotting
Ap.T_on <- rbind(A22.high.T_on, Ar.high.T_on, A22.low.T_on, Ar.low.T_on)

@@

Next, I partition the differences in the reaction norms into the variation explained by differences in the trait means and slope, as curvature and wiggle did not differ between species.

@@

```{r extract_Transcripts_only}
A22.only.high <- Ap.response.type[which(Ap.response.type$A22.type == "High" & Ap.response.type$Ar.type != "High"), "Transcript"]
Ar.only.high <- Ap.response.type[which(Ap.response.type$A22.type != "High" & Ap.response.type$Ar.type == "High"), "Transcript"]

@@

#for(i in unique(A22.low.Ar.int.TPM.dt.sub$Transcript)[1:10]) {
#    s <- A22.low.Ar.int.TPM.dt.sub[i]
#    X11()
#    plot(s$val, s$pTPM, ylim = c(0, max(s$pTPM)+.1))
#    points(s$val, s$TPM, pch = 8, col = "red")
#    if(s[which(s$val == 38.5) , pTPM] == min(s$pTPM)) print("OffHigh"#) else {
#        print("OnLow")
#    }
#}

@@

```{r rData, echo=FALSE}
# save RData for manuscript file
save(RxNpval, sigtable, chi1, resp.TPM.dt.sub, Ap.type.table, tt2, tt3, qlslope, qlmean, GO.stress.Xsq, GO0006950.responsive, Ap.df, w1, w2, w3, Ap.T_on, Ap.BP.resultParentChild, Ap.gsea1, Ap.setdiff.gsea, resp.stress.responsive.count, t.mean, t.slope, t.curvature, t.wiggle, t.themsens, t.thermbreadth, file = "ms.RData")
```
